### 2014-09-26 thesis/experiments/experiments.tex
Finished basic writeup of experimental setup #12

\subsection{Ensemble classifiers}

\section{Performance evaluation} % don't forget cross-validation
\label{sec:perfeval}

\subsection{Metrics}

\subsection{Statistical tests}

>>>>

\subsection{Ensemble classifiers}
In order to improve upon the performance of individual classifiers, we also
tested the performance of ensembles of classifiers -- that is, combining the
predictions of several different classifiers, or several of the same
classifier. Specifically, the ensemble methods used were:
\begin{itemize}
  \item Random Forests
  \item Bagging
  \item Stacked generalisation (stacking)
  \item Boosting (AdaBoostM1)
\end{itemize}

Again, we were able to create predictive models using the implementations of
these ensemble methods in WEKA 3.7.11. Since ensemble classifiers are not
actual classifiers but a way to train and combine the predictive power of more
than one classifier, we list the combinations of classifiers used in our
ensemble methods:
\todo{insert table!}

\section{Performance evaluation} % don't forget cross-validation
\label{sec:perfeval}
Here we describe the methods used in order to assess the performance of the
models constructed through single classifiers and ensemble methods described
above.

\subsection{Metrics}
There are many available and commonly used metrics that we can use when
evaluating and comparing the performance of prediction models. The ones that
we use are: \todo{maybe put these in a table}
\begin{itemize}
  \item Accuracy
  \item Specificity
  \item Sensitivity
  \item Area under the receiver-operating characteristic (ROC) curve, or AUC
\end{itemize}

Since we only have one data set, we use ten-fold stratified cross-validation
to obtain values for the above metrics. We run the ten-fold cross-validation
40 times for each classifier (single or ensemble) for each of the 7 data sets
produced from feature selection. 40 runs was necessary in order for us to
compute confidence intervals for each of the metrics, which makes use of the
Central Limit Theorem from statistics.

\subsubsection{Confidence intervals}
In order to compare our results with that of Dinh et. al. \citep{Dinh2013a},
we are especially interested in the mean cross-validated AUC of our
classifiers as well as
the upper and lower bounds of the 95\% confidence interval associated with this
mean. The intervals are constructed using this argument:

For each classifier, let the population of all of its ten-fold cross-validated
AUC scores be some random variable $X$, which follows a distribution whose
parameters (such as mean and standard deviation) we do not know.
The Central Limit Theorem states that given a random
sample of $n$ items from $X$, namely $X_1,X_2,\dots,X_n$, the sample mean
$\bar{x}$
is approximately normally distributed when $n$ is at least roughly around 30
and the $X_i$'s are independent and identically distributed.
Consequently, we can construct a $(1-\alpha)$\% confidence interval for
$\bar{x}$ -- where $\alpha$ is commonly called the
\textit{significance level} -- as follows:
\begin{equation}
  \left[\bar{x} - z_{1-\alpha/2}\dfrac{s}{\sqrt{n}},
    \bar{x} + z_{1-\alpha/2}\dfrac{s}{\sqrt{n}}\right]
\end{equation}
where $\bar{x}$ is the sample mean, $\alpha$ is the significance level
(5\% or $0.05$ in our case), $s$ is the sample standard deviation, $n$
is the number of observations in our sample, and $z_{1-\alpha/2}$ is the value
of the standard normal variable $Z \sim \mathcal{N}(0,1)$ with cumulative
probability $1-\alpha/2$. Since we have taken 40 independent samples of the
ten-fold cross-validated AUC, the Central Limit Theorem holds and we can
compute the mean and standard deviation of our 40 samples in order to
construct a 95\% confidence interval for the mean AUC of each classifier.

\subsection{Statistical tests}
To decide whether or not the difference in values of each metric between
classifiers was statistically significant, paired $t$-tests were conducted for
a subset of the results: \todo{elaborate}
\begin{itemize}
  \item Some feature set vs other feature set
  \item Single classifier vs other single classifier
  \item Ensemble vs single
  \item Our best method vs Dinh2013's method
\end{itemize}
